---
output: rmarkdown::github_document
---

`tlsobs` : Tools to Work with the 'Mozilla' 'TLS' Observatory 'API'

The Mozilla [TLS Observatory](https://observatory.mozilla.org/analyze.html) can be used to compare your site against the Mozilla guidelines. You can use their service or [host your own](https://github.com/mozilla/tls-observatory#getting-started). Both the central service and locally hosted services have an API. Either the central service or a local service can be queried from the functions provided.

The following functions are implemented:

- `get_cert`:	Retrieve a certificate
- `get_issuer_count`:	Retrieve certificate issuer count
- `get_paths`:	Retrieve paths from a certificate to one of multiple roots.
- `get_scan_results`:	Retrieve a certificate
- `get_usage_stats`:	Retrive 24 hour scan statistics from the TLS Obsercatory API
- `get_heartbeat`:	Check for TLS Obsercatory API server online status

### TODO

- Starting a scan (<https://github.com/mozilla/tls-observatory#post-apiv1scan>)
- Publishing a certificate (<https://github.com/mozilla/tls-observatory#post-apiv1certificate>)
- Retrieving a trust store (<https://github.com/mozilla/tls-observatory#get-apiv1truststore>)
- firing up a local Docker version and testing against it.

Feel free to implement any of ^^. Please file an issue if you do and ensure you update `DESCRIPTION`

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/tlsobs")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(tlsobs)

# current verison
packageVersion("tlsobs")

get_heartbeat()

str(get_cert(1))

str(get_issuer_count(1))

str(get_paths(1))

str(get_scan_results("12302333"))
```

```{r cache=TRUE}
get_usage_stats()
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
